Modern Graph Generators: A Survey

### 2018-11-26 challenges.tex
Sherif Changes

Concerning the former, analyzing and labeling structural networks is
deemed to be more difficult for graph datasets in the presence of noise.
Since de-noising graph data is difficult to achieve, several machine learning
techniques have been adapted to work with noise (i.e. mislabeled
samples) or outliers, such as
imbalanced graph classification \cite{PanZ13} and
binary graph classification with positive and negative weights \cite{CheungSML16}.
Synthetic graph generators that take into account noisy and missing data
have been studied in \cite{NamataG10}, where graph identification is presented in
order to  model the inference of a cleaned output network from a
noisy input graph.
Concerning the latter, data quality techniques handling graph data are recently considering ad-hoc
generation of graph data and graph quality rules in order to assess the
effectiveness of error detection and data repairing algorithms \cite{FanWX16a,AriouaB18}. The
corresponding graph quality rules are typically handcrafted by domain
experts, whereas an automatic generation of such rules along with the graph
data generation in tandem would be an interesting future challenge for the
community.

>>>>

Concerning the former, analyzing and labeling structural networks is
deemed to be more difficult for graph datasets in the presence of noise.
Since de-noising graph data is difficult to achieve, various machine learning-based 
approaches have been adapted to work with noise (i.e. mislabeled
samples) or outliers, such as
imbalanced graph classification \cite{PanZ13} and
binary graph classification with positive and negative weights \cite{CheungSML16}.
Synthetic graph generators that take into account noisy and missing data
have been studied in \cite{NamataG10}, where graph identification is presented in
order to  model the inference of a cleaned output network from a
noisy input graph.
Concerning the latter, data quality techniques handling graph data are recently considering ad-hoc
generation of graph data and graph quality rules in order to evaluate the
effectiveness of error detection and data repairing algorithms \cite{FanWX16a,AriouaB18}. The
corresponding graph quality rules are typically handcrafted by domain
experts, whereas an automatic generation of such rules along with the graph
data generation in tandem would be an interesting future challenge for the
community.

### 2018-11-26 comparison.tex
Sherif Changes

In order to provide the reader with a quick preview of the generators and  to enable finding the target solutions easily, we start the survey with a  classification and comparative study of the existing tools. In general, there are various ways to classify them. We first provide an overview of the approaches used in related work after which we then introduce our approach. As mentioned in the Introduction, since this survey is unique especially in terms of scope, our classification and comparative strategy differs as well.

>>>>

In order to provide the reader with a general preview of the generators and  to enable finding the target solutions easily, we start the survey with a  classification and comparative study of the existing tools. In general, there are various ways to classify them. We first provide an overview of the approaches used in related work after which we then introduce our approach. As mentioned in the Introduction, since this survey is unique especially in terms of scope, our classification and comparative strategy differs as well.

### 2018-11-26 generators_GraphDatabases.tex
Sherif Changes

Currently there exists a number  of papers which compare the efficiency of graph databases with regards to distinct use cases, such as  the community detection problem~\cite{Beis2015}, social tagging systems~\cite{Giatsoglou2011}, graph traversal~\cite{Ciglan:2012:BTO:2374486.2375242}, graph pattern matching~\cite{Pobiedina2014}, data provenance~\cite{Vicknair:2010:CGD:1900008.1900067}, or even several distinct use cases~\cite{Grossniklaus2013Towar-24253}. However, the number of graph data generators and benchmarks that have been designed specifically for graph databases is relatively small. Either a general graph generator is used for benchmarking graph databases, such as, e.g., the HPC Scalable Graph Analysis Benchmark~\cite{Dominguez-Sal:2010:SGD:1927585.1927590} or the graph DBMS benchmarking tools are designed in a more general scope. Hence it is questionable whether a benchmark  that is targeted specifically for graph databases is necessary. \cite{Dominguez-Sal:2010:DDG:1946050.1946053} discussed this question and related topics. On the basis of a review of applications of graph databases (namely, social network analysis,  genetic interactions, recommendation systems, and travel planning and routing), the authors analyzed and discussed the characteristics of the graphs that appear in such applications and how they could influence benchmarking, different types of operations used in these applications and the characteristics of the evaluation setup of the benchmark. In this section, we focus on graph data generators and benchmarks that have been primarily targeting graph DBMSs.

>>>>

Currently there exists a number  of papers which compare the efficiency of graph databases with regards to distinct use cases, such as  the community detection problem~\cite{Beis2015}, social tagging systems~\cite{Giatsoglou2011}, graph traversal~\cite{Ciglan:2012:BTO:2374486.2375242}, graph pattern matching~\cite{Pobiedina2014}, data provenance~\cite{Vicknair:2010:CGD:1900008.1900067}, or even several distinct use cases~\cite{Grossniklaus2013Towar-24253}. However, the number of graph data generators and benchmarks that have been designed specifically for graph databases is relatively small. Either a general graph generator is used for benchmarking graph databases, such as, e.g., the HPC Scalable Graph Analysis Benchmark~\cite{Dominguez-Sal:2010:SGD:1927585.1927590} or the graph DBMS benchmarking tools are designed in a more general scope. Hence it is questionable whether a benchmark  that is targeted specifically for graph databases is necessary. \cite{Dominguez-Sal:2010:DDG:1946050.1946053} discussed this question and related topics. On the basis of a review of applications of graph databases (namely, social network analysis,  genetic interactions, recommendation systems, and travel planning and routing), the authors analyzed and discussed the features of the graphs for these types of applications and how they could affect the benchmarking process, different types of operations used in these applications and the characteristics of the evaluation setup of the benchmark. In this section, we focus on graph data generators and benchmarks that have been primarily targeting graph DBMSs.

### 2018-11-26 generators_LinkedData.tex
Sherif Changes

\paragraph{BSBM} The Berlin SPARQL Benchmark (BSBM)\footnote{\url{http://wifo5-03.informatik.uni-mannheim.de/bizer/berlinsparqlbenchmark/}}, is centered around an e-commerce application domain with object types such as \emph{Customer}, \emph{Vendor}, \emph{Product} and \emph{Offer} in addition to the relationship among them~\cite{Bizer09theberlin}.
The benchmark provides a workload that have 12 queries with 2 types of query workloads (i.e., 2 sequences of the 12 queries) emulating the navigation pattern and search of a consumer seeking a product. The data generator is capable of producing arbitrarily scalable datasets by controlling the number of products ($n$) as a scale factor.  The scale factor also impacts other data characteristics, such as, e.g., the depth of type hierarchy of products (defined as $d = round(log_{10}(n))/2 + 1$), branching factor ($bfr = 2 \times round(log_{10}(n))$), the number of product features (having $lowerBound = 35 \times i / (d \times (d+1)/2 - 1)$ and $upperBound = 75 \times i / (d \times (d+1)/2 - 1)$) etc. BSBM can output two representations, i.e. an RDF representation along with a relational representation. Thus, BSBM also defines an SQL~\cite{sql} representation of the queries. This allows comparison of SPARQL~\cite{sparql} results  to be compared against the performance of traditional RDBMSs.

@@

\paragraph{DBPSB} DBpedia SPARQL Benchmark (DBPSB)\footnote{\url{http://aksw.org/Projects/DBPSB.html}} proposed at the University of Leipzig has been designed using workloads that have been issued by humans and applications over existing RDF data~\cite{Morsey2011,Morsey:2012:UBR:2900929.2901031}. In addition, the authors argue that benchmarks like LUBM, BSBM, or SP$^2$Bench resemble relational database benchmarks involving relational data structures with few and homogeneously structured classes, whereas, in reality, RDF datasets are increasingly heterogeneous. For example, DBpedia version 3.6 consists of 289,016 classes of which 275 classes are defined based on the DBpedia ontology. In addition, different datatypes and object references of various types are
used in property values. Hence, they presented a universal SPARQL benchmark generation approach which uses a flexible data production mechanism that mimics the input data source. This dataset generation process begins using an input dataset then multiple datasets with different sizes  are then generated by duplicating all the RDF triples with changing their namespaces.  For generating smaller datasets, an adequate selection of all triples is selected randomly or using a sampling mechanism over the various classes in the dataset. \iffalse The goal of the query analysis and clustering is to detect prototypical queries on the basis of their frequent usage and similarity.\fi The methodology is applied on the DBpedia SPARQL endpoint and a set of 25 SPARQL query templates is derived, that cover the frequently used SPARQL features.

@@

\paragraph{Geographica} The Geographica benchmark\footnote{\url{http://geographica.di.uoa.gr/}} has been designed to target the area of geospatial data~\cite{DBLP:conf/semweb/GarbisKK13} and respective SPARQL extensions GeoSPARQL~\cite{battle2012enabling} and stSPARQL~\cite{koubarakis2010modeling}. The benchmark involves a real-world workload that uses openly available datasets that cover a range of geometry types (e.g., points, lines, polygons) and  a synthetic workload. In the former case there is a (1) a micro benchmark that tests primitive spatial functions (involving 29 queries) and (2) macro benchmark that tests the performance of RDF engines in various application scenarios such as  map exploring and search (consisting of 11 queries). In the latter case of a synthetic workload the generator produces synthetic datasets of different sizes that corresponds to an ontology based on OpenStreetMap  and instantiates query templates. \iffalse The spatial extent of the land ownership dataset constitutes a uniform grid of $n \times n$ hexagons, whereas the size of each dataset is given relatively to $n$.\fi The generated SPARQL query workload is corresponding to spatial selection and spatial joins by instantiating 2 query templates.

>>>>

\paragraph{BSBM} The Berlin SPARQL Benchmark (BSBM)\footnote{\url{http://wifo5-03.informatik.uni-mannheim.de/bizer/berlinsparqlbenchmark/}}, is centered around an e-commerce application domain with object types such as \emph{Customer}, \emph{Vendor}, \emph{Product} and \emph{Offer} in addition to the relationship among them~\cite{Bizer09theberlin}.
The benchmark provides a workload that have 12 queries with 2 types of query workloads (i.e., 2 sequences of the 12 queries) emulating the navigation pattern and search of a consumer seeking a product. The data generator is capable of producing arbitrarily scalable datasets by controlling the number of products ($n$) as a scale factor.  The scale factor also impacts other data characteristics, such as, e.g., the depth of type hierarchy of products, branching factor, the number of product features,..., etc. BSBM can output two representations, i.e. an RDF representation along with a relational representation. Thus, BSBM also defines an SQL~\cite{sql} representation of the queries. This allows comparison of SPARQL~\cite{sparql} results  to be compared against the performance of traditional RDBMSs.

@@

\paragraph{DBPSB} DBpedia SPARQL Benchmark (DBPSB)\footnote{\url{http://aksw.org/Projects/DBPSB.html}} proposed at the University of Leipzig has been designed using workloads that have been issued by humans and applications over existing RDF data~\cite{Morsey2011,Morsey:2012:UBR:2900929.2901031}. In addition, the authors argue that benchmarks like LUBM, BSBM, or SP$^2$Bench resemble relational database benchmarks involving relational data structures with few and homogeneously structured classes, whereas, in reality, RDF datasets are increasingly heterogeneous. For example, DBpedia version 3.6 consists of 289,016 classes of which 275 classes are defined based on the DBpedia ontology. In addition, different data types and object references of the various types are
used in property values. Hence, they presented a universal SPARQL benchmark generation approach which uses a flexible data production mechanism that mimics the input data source. This dataset generation process begins using an input dataset then multiple datasets with different sizes  are then generated by duplicating all the RDF triples with changing their namespaces.  For generating smaller datasets, an adequate selection of all triples is selected randomly or using a sampling mechanism over the various classes in the dataset. \iffalse The goal of the query analysis and clustering is to detect prototypical queries on the basis of their frequent usage and similarity.\fi The methodology is applied on the DBpedia SPARQL endpoint and a set of 25 SPARQL query templates is derived to cover the frequently used SPARQL features.

@@

\paragraph{Geographica} The Geographica benchmark\footnote{\url{http://geographica.di.uoa.gr/}} has been designed to target the area of geospatial data~\cite{DBLP:conf/semweb/GarbisKK13} and respective SPARQL extensions GeoSPARQL~\cite{battle2012enabling} and stSPARQL~\cite{koubarakis2010modeling}. The benchmark involves a real-world workload that uses openly available datasets that cover a range of geometry types (e.g., points, lines, polygons) and  a synthetic workload. In the former case there is a (1) a micro benchmark that evaluates primitive spatial functions (involving 29 queries) and (2) macro benchmark that tests the performance of RDF engines in various application scenarios such as  map exploring and search (consisting of 11 queries). In the latter case of a synthetic workload the generator produces synthetic datasets of different sizes that corresponds to an ontology based on OpenStreetMap  and instantiates query templates. \iffalse The spatial extent of the land ownership dataset constitutes a uniform grid of $n \times n$ hexagons, whereas the size of each dataset is given relatively to $n$.\fi The generated SPARQL query workload is corresponding to spatial selection and spatial joins by instantiating 2 query templates.

### 2018-11-26 generators_SocialNetworks.tex
Sherif Changes

\paragraph{Realistic Social Network}
~\cite{Barrett:2009:GAL:1995456.1995598} focused on the construction of
realistic social networks. For this purpose the authors combine both public and private data sets
with large-scale agent based techniques. The process works as follows: In the first step
it creates a synthetic population by integrating public and commercial databases. In the second step, it determines a set of activity templates. A 24-hour activity sequence including
geolocations is assigned to each synthetic individual. To demonstrate the approach, the authors create a synthetic US population consisting of people and households together with respective geolocations. For this purpose the authors combine simulation and data fusion techniques utilizing various real-world data sources such as U.S. Census data, responses to an activity survey or a time-use survey. %Demographic information for each person and location, a minute-by-minute schedule of each person's activities, and the locations where these activities take place is generated by a combination of simulation and data fusion techniques.
The result is captured by a dynamic social contact network. Similar methods for agent-based strategies have been reported in~\cite{Bernstein:2013:SAS:2499604.2499609}.

@@

\paragraph{Cloning of Social Networks} ~\cite{Sukthankar-SocialInfo2014}
introduced a synthetic network generator designed for cloning social network
statistics of an existing dataset. The network starts with a small number of
nodes, and new nodes are added until the network reaches the required number. It
has two basic parameters: homophily and link density. A high \emph{homophily}
value indicates that links are more likely to be formed between nodes with the
same label; these labels can be viewed as being equivalent to community
membership.

>>>>

\paragraph{Realistic Social Network}
~\cite{Barrett:2009:GAL:1995456.1995598} focused on the construction of
realistic social networks. For this purpose the authors combine both public and private data sets
with large-scale agent-based techniques. The process works as follows: In the first step
it generates a synthetic data by combining public and commercial databases. In the second step, it determines a set of activity templates. A 24-hour activity sequence including
geolocations is assigned to each synthetic individual. To demonstrate the approach, the authors create a synthetic US population consisting of people and households together with respective geolocations. For this purpose the authors combine simulation and data fusion techniques utilizing various real-world data sources such as U.S. Census data, responses to an activity survey or a time-use survey. %Demographic information for each person and location, a minute-by-minute schedule of each person's activities, and the locations where these activities take place is generated by a combination of simulation and data fusion techniques.
The result is captured by a dynamic social contact network. Similar methods for agent-based strategies have been reported in~\cite{Bernstein:2013:SAS:2499604.2499609}.

@@

\paragraph{Cloning of Social Networks} ~\cite{Sukthankar-SocialInfo2014}
introduced a synthetic network generator designed for cloning social network
statistics of an existing dataset. The network starts with a small number of
nodes, and new nodes are added until the network reaches the required number. It
has two basic parameters: homophily and link density. A high \emph{homophily}
value reflects that links have higher chances to be established among the nodes with the
same label; these labels can be considered as being equivalent to community
membership.

### 2018-11-26 generators_analytics.tex
Sherif Changes

\paragraph{HPC Scalable Graph Analysis Benchmark} The HPC Scalable Graph
Analysis Benchmark~\cite{HPCgraph,Bader:2005:DIH:2099301.2099360} consists of a
weighted, directed graph that follows a power-law distribution and four related
analysis techniques (namely graph construction, graph extraction with BFS,
                     classification of large vertex sets, and graph analysis
                     with betweenness centrality). The generator has the
following parameters: the number of vertices, the number of edges, and maximum weight of
an edge. It outputs a list of tuples containing identifiers of vertices of an
edge (with the direction from the first one to the second one) and weights
(positive integers  with a uniform random distribution) assigned to the edges of
the multigraph.  The algorithm of the generator is based on R-MAT. To reduce the data
locality, the vertex ids are randomly permuted and the output
tuples are shuffled. A related project from the same authors
developed for the 9th DIMACS Shortest Paths Challenge is GTgraph~\cite{GTgraph}.
It involves three types of graphs: (1) Erd\"{o}s-R\'{e}nyi random graphs, (2)
different graphs from the DARPA HPCS SSCA\#2 graph theory benchmark
(version 1.0), and (3) small-world graphs generated using the R-MAT graph
generator.

>>>>

\paragraph{HPC Scalable Graph Analysis Benchmark} The HPC Scalable Graph
Analysis Benchmark~\cite{HPCgraph,Bader:2005:DIH:2099301.2099360} consists of a
weighted, directed graph that has a power-law distribution and four related
analysis techniques (namely graph construction, graph extraction with BFS,
                     classification of large vertex sets, and graph analysis
                     with betweenness centrality). The generator has the
following parameters: the number of nodes, the number of edges, and maximum weight of
an edge. It outputs a list of tuples containing identifiers of vertices of an
edge (with the direction from the first one to the second one) and weights
(positive integers  with a uniform random distribution) assigned to the edges of
the multigraph.  The algorithm of the generator is based on R-MAT. To reduce the data
locality, the vertex ids are randomly permuted and the output
tuples are shuffled. A related project from the same authors
developed for the 9th DIMACS Shortest Paths Challenge is GTgraph~\cite{GTgraph}.
It involves three types of graphs: (1) Erd\"{o}s-R\'{e}nyi random graphs, (2)
different graphs from the DARPA HPCS SSCA\#2 graph theory benchmark
(version 1.0), and (3) small-world graphs generated using the R-MAT graph
generator.

### 2018-11-26 generators_community_detection.tex
Sherif Changes

Community detection is one of the many graph analytics algorithms typically used
on domains such as social networks or bioinformatics. Communities are groups of
vertices that are highly connected among them, while being scarcely connected to
the rest of the graph. Such communities emerge from the fact that real graphs
are not random, but follow real-world dynamics that make similar entities to
have a larger probability to be connected. As a consequence, detected
communities are used to reveal vertices with similar characteristics, for
instance to discover functionally equivalent proteins in protein-protein
interaction networks, or persons with similar interests in social networks. Such
applications have made community detection a hot topic during the last fifteen
years with tens of developed algorithms and detection
strategies~\cite{doi:10.1002/wics.1403,Kim:2015:CDM:2854006.2854013}. For
comparing the quality of the different proposed techniques, one needs graphs
with \emph{reference communities}, that is, communities known beforehand. Since
it is very difficult to have large real graphs with reference communities
(mainly because these would require a manual labeling), graphs for benchmarking
community detection algorithms are typically generated synthetically.

@@

\paragraph{LFR} Lancichinetti, Fortunato
and Radicchi (hence LFR)~\cite{PhysRevE.78.046110} propose a class of benchmark
graphs for community detection where communities are of different sizes and
densities. The generator generates communities of various sizes following a
power-law distribution whose parameters can be configured. The degree of the
nodes is also sampled from a power-law distribution. Additionally, the generator
introduces the concept of the ``mixing factor'', which consists of the fraction of
edges in the graph connecting nodes that belong to different communities. Such parameter
allows  the degree of modularity of the generated graph  to be tuned, thus
testing the robustness of the algorithms under different conditions. The
generation process starts with an empty graph and incrementally fills in the
adjacency matrix by considering the described constraints.

>>>>

Community detection is one of the many graph analytics algorithms typically used
on domains such as social networks or bioinformatics. Communities are groups of nodes that are highly connected among them, while being scarcely connected to
the rest of the graph. Such communities emerge from the fact that real graphs
are not random, but follow real-world dynamics that make similar entities to
have a larger probability to be connected. As a consequence, detected
communities are used to reveal vertices with similar characteristics, for
instance to discover functionally equivalent proteins in protein-protein
interaction networks, or persons with similar interests in social networks. Such
applications have made community detection a hot topic during the last fifteen
years with tens of developed algorithms and detection
strategies~\cite{doi:10.1002/wics.1403,Kim:2015:CDM:2854006.2854013}. For
comparing the quality of the different proposed techniques, one needs graphs
with \emph{reference communities}, that is, communities known beforehand. Since
it is very difficult to have large real graphs with reference communities
(mainly because these would require a manual labeling), graphs for benchmarking
community detection algorithms are typically generated synthetically.

@@

\paragraph{LFR} Lancichinetti, Fortunato
and Radicchi (hence LFR)~\cite{PhysRevE.78.046110} propose a class of benchmark
graphs for community detection where communities are of different sizes and
densities. The generator generates communities of various sizes with a
power-law distribution whose parameters can be configured. The degree of the
nodes is also sampled from a power-law distribution. Additionally, the generator
introduces the concept of the ``mixing factor'', which consists of the percentage of
edges in the graph connecting nodes that belong to different communities. Such parameter
allows  the degree of modularity of the generated graph  to be tuned, thus
testing the robustness of the algorithms under different conditions. The
generation process starts with an empty graph and incrementally fills in the
adjacency matrix by considering the described constraints.

### 2018-11-26 generators_general.tex
Sherif Changes

\paragraph{Darwini} Darwini~\cite{edunov2016darwini} is an extension of BTER
designed to run on Vertex Centric computing frameworks like
Pregel~\cite{malewicz2010pregel} or Apache Giraph~\cite{ching2015one}, with the
additional feature that it is more accurate when reproducing the clustering
coefficient of the input graph. Instead of just focusing on the average
clustering coefficient for each degree, Darwini is able to model the clustering
coefficient distribution per degree. It achieves this by gathering the vertices
of the graph into buckets based on the expected number of closed triangles that they need
to close in order to attain the expected clustering coefficient. The latter is
sampled from the input distributions. Then, the vertices in each bucket are
connected randomly with a probability that would produce the expected
desired number of triangles for each bucket. Then, as in BTER, the excess degree
is used to connect the different buckets. The authors report that Darwini is
able to generate graphs with billions and even trillions of edges.

>>>>

\paragraph{Darwini} Darwini~\cite{edunov2016darwini} is an extension of BTER
designed to run on Vertex Centric computing frameworks like
Pregel~\cite{malewicz2010pregel} or Apache Giraph~\cite{ching2015one}, with the
additional feature that it is more accurate when reproducing the clustering
coefficient of the input graph. Instead of just focusing on the average
clustering coefficient for each degree, Darwini is able to model the clustering
coefficient distribution per degree. It achieves this by gathering the nodes
of the graph into buckets based on the expected number of closed triangles that they need
to close in order to attain the expected clustering coefficient. The latter is
sampled from the input distributions. Then, the vertices in each bucket are
connected randomly with a probability that would produce the expected
desired number of triangles for each bucket. Then, as in BTER, the excess degree
is used to connect the different buckets. The authors report that Darwini is
able to generate graphs with billions and even trillions of edges.

### 2018-11-26 introduction.tex
Sherif Changes

\paragraph*{Contributions} Our survey revisits the representatives of
modern graph data generators and summarizes their major features. The comprehensive review and analysis make this paper useful for motivating new graph data generation techniques as well as serving as a technical reference for selecting suitable solutions. In particular, the introductory categorization and comparative study enables the reader to quickly get his/her bearings in the field and identify a subset of generators of his/her interest. Since we do not limit the survey to a particular area of graph data management,  the reader can get a broader scope in the field. Hence, while practitioners can find a solution in another previously unexpected area, researchers can identify new target areas or exploit successful results in new fields. Last but not least, to provide a global view of the state-of-the-art, we also provide an overview of most commonly used real-world testing graph data sets. And, finally, we identify general open problems of graph data synthesis and indicate possible solutions to show that it still forms a challenging and promising research area.

@@

Aggarwal and Subbian \cite{AggarwalS14} have surveyed the evolution of analysis in
graphs, by primarily focusing on data mining maintenance methods and on analytical
quantification and explanation of the changes of the underlying networks.
A brief discussion on evolutionary
network data generators is carried out in
the paper. The data generation of evolutionary networks is based on
Densification Power Law (DPL) and shrinking diameters and community-guided
attachment properties \cite{Leskovec:2005:GOT:1081870.1081893} is then considered, along with tackling Kronecker
recursion with recursive tensor multiplication \cite{AkogluMF08}.
We refer the reader to this survey for evolutionary network generators and
we further discuss the open challenges of evolving graph data in Section 5.
%\TODO{Better highlight the differences when Sherif's part is in.}

>>>>

\paragraph*{Contributions} Our survey revisits the representatives of
modern graph data generators and summarizes their major features. The comprehensive review and analysis make this paper useful for motivating new graph data generation techniques as well as serving as a technical reference for selecting suitable solutions. In particular, the introductory categorization and comparative study enables the reader to quickly get his/her bearings in the field and identify a subset of generators of his/her interest. Since we do not limit the survey to a particular area of graph data management,  the reader can get a broader scope in the field. Hence, while practitioners can find a solution in another previously unexpected area, researchers can identify new target areas or exploit successful results in new fields. Last but not least, to provide a global view of the state-of-the-art, we also provide an overview of most commonly used real-world testing graph datasets. And, finally, we identify general open problems of graph data synthesis and indicate possible solutions to show that it still forms a challenging and promising research area.

@@

Aggarwal and Subbian~\cite{AggarwalS14} have surveyed the evolution of analysis in
graphs, by primarily focusing on data mining maintenance methods and on analytical
quantification and explanation of the changes of the underlying networks.
A brief discussion on evolutionary
network data generators is carried out in
the paper. The data generation of evolutionary networks is based on
Densification Power Law (DPL) and shrinking diameters, community-guided
attachment properties~\cite{Leskovec:2005:GOT:1081870.1081893}.
Generation of graphs tackling Kronecker
recursion with recursive tensor multiplication~\cite{AkogluMF08} is then considered in the above survey.
We refer the readers to the aforementioned survey for evolutionary network generators and further discuss the open challenges of evolving graph data in Section 5.
%\TODO{Better highlight the differences when Sherif's part is in.}
